---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data


If the Comma Seperated CSV file does not exist than extract it from the zip file to a data directory

```{r}
if(!file.exists("./data/activity.csv")){
                # extract the file to the data folder
                unzip("activity.zip", exdir = "data", overwrite=TRUE)
}
```

Load the data into an activity variable

remove the NAs in the steps column
```{r}
activity <- read.csv("data/activity.csv")
activityWithoutNAs <- activity[!is.na(activity$steps),]
```

## What is mean total number of steps taken per day?

Calculate the total number of steps per day

1. Load necessary packages

2. Remove NAs

3. Group by day

4. Summarise total of steps per day

5. Draw a histogram.
```{r}
require(dplyr)
grp <- filter(activity,!is.na(steps)) %>%group_by(day=date) %>% summarise(total=sum(steps))
hist(grp$total, main="Histogram of Total number\nof Steps per Day", xlab="Total Number of Steps")
```

Mean of the total number of steps per day
```{r}
mean(grp$total)
```

Median of the total number of steps per day
```{r}
median(grp$total)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?


Reset the working directory
```{r}
setwd(old.dir)
```